---
title: "Capital gains derived by non-residents"
author: "Frederik Heitmüller"
date: "2022-10-11"
output: html_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)

if (!require('here')) install.packages('here'); library('here') 
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
if (!require('magrittr')) install.packages('magrittr'); library('magrittr') 
if (!require('countrycode')) install.packages('countrycode'); library('countrycode') 
if (!require('purrr')) install.packages('purrr'); library('purrr') 
if (!require('stringr')) install.packages('stringr'); library('stringr') 

devtools::load_all()

# defining for which data years the script should run
years <- c(2004:2021)

```

Rates for four different types of capital gains were extracted from the EY Corporate Tax Guides by hand and cross-checked by the researcher. 
The four different types coded are:
- “sales of shares of land-rich companies”
- “sales of shares”; 
- “indirect sales of shares of land-rich companies”
- “indirect sales of shares”.

Capital gains tax legislation varies significantly between countries. Some countries levy capital gains taxes as part of the general income tax, whereas other countries have specific legislation, apply differential rates or exempt certain items or taxpayers from capital gains taxation. Hence, a number of decisions had to be taken to produce a comparable data set. The idea behind decisions was to compare the treatment that would apply to the bulk of transactions undertaken by multinational enterprises that invest in developing countries.

- If there is a differentiation between sales by residents and by non-residents, the rate applicable to sales by non-residents was coded. 
- If there is a differentiation between sales by non-residents with permanent establishment in the country and sales by non-residents without permanent establishment, then the treatment for non-residents without permanent establishment is coded.
- If there is a differentiation for shares traded on stock-exchanges and shares of private companies, the rate for sales of shares for private companies was coded. 
- If there is a differentiation between short-term and long-term gains, the rate for long-term gains was coded. 2 years was retained as cut-off, since this is what is often used by countries. 
- If there is a differentiation between sales of shares from portfolio investment and shares from direct investment (holdings of less or more than a certain percentage, usually 10%), the rate for sales of shares from direct investment was coded. 
- If there is a monetary threshold above which a higher rate applies, that higher rate is coded
- Where a company can elect between a net capital gains tax rate and a gross withholding rate, the rate for net income is coded, as this is likely to be the more beneficial rate most of the time. If only a gross withholding rate is available, then that rate was entered.
- Where the disposal of shares in only certain types of companies is taxed (e.g. only in the mineral sector), then imposition on gains of "land-rich" companies is coded as "yes" or where a higher rate to this type of property applies, the higher rate is retained.
- Conversely, where only the gains derived by certain types of companies other than in sectors dealing with immovable property (e.g. in the financial sector) are taxed, then an exemption is coded, since MNEs retain choices
- Where non-residents are only taxed when situated in low-tax jurisdictions or "tax havens", this is not coded, since it is unlikely that a country would sign a tax treaty with such a jurisdiction or that the ultimate beneficiary of the income would reside in such a jurisdiction. Hence one would not expect a treaty shopping risk because of the differential treatment in these jurisdictions. 

A conceptually difficult question is how the cases should be coded where the description simply states that "capital gains are included in ordinary income" (or a similar phrase). The first intuition is to suppose that this would include gains derived by non-residents from local companies. However, if the domestic law contains a provision stating that non-residents are only taxed if they have a permanent establishment in the country and are not taxed on the total income, then gains derived by non-residents would probably not be taxed. If instead, domestic law contains a more general provision, that subjects all income derived within the jurisdiction to tax, then it seems more likely that gains by non-residents from sales of shares are taxed.
Even in that case, however, it is possible that in practice this right is not enforce due to the difficulty in detecting the sale. 
Only if the sale needs to be registered.


```{r cap gains taxes hand detailed}

cap_gain <- read_csv(here("data-created/capital_gains_ey.csv"))
stat_rates <- read_csv(here("data-created/ey_stat_rates.csv"))

# further cleaning
#Canada has specific paragraphs on non-residents, so the others need to be eliminated
cap_gain <- cap_gain[-which(cap_gain$iso3c == "CAN" & str_detect(str_sub(cap_gain$text, 1, 24), "Capital gains and losses|Capital Gains and Losses")), ]
cap_gain <- cap_gain[-which(cap_gain$iso3c == "CRI" & str_detect(str_sub(cap_gain$text, 1, 18), "Capital Income Tax")), ]

cap_gain %<>% group_by(iso3c) %>% arrange(year, .by_group = TRUE)
cap_gain %<>% mutate(text = coalesce(text, corp_tax_expl))
cap_gain$text %<>% trimws()

cap_gain %<>% mutate(text_same = NA)
for (i in 2:nrow(cap_gain)) {
  if (cap_gain$text[i] == cap_gain$text[i - 1]) {
    cap_gain$text_same[i] <- "same" 
  } else {
    cap_gain$text_same[i] <- "change" 
  }
}

cap_gain %<>% mutate(no_sent = str_count(text, pattern = "\\."))
cap_gain %<>% mutate(nonresident = str_detect(text, "Nonresident|nonresident|Non-resident|non-resident|foreign|Foreign"))
cap_gain %<>% mutate(not_taxed = str_detect(text, "Capital gains are not tax|Capital gains are not subject to tax|Capital gains are exempt from|does not impose a capital gains|does not impose a Capital Gains|does not impose capital gains tax|does not impose a tax on"))
cap_gain %<>% mutate(indirect = str_detect(text, "Indirect|indirect|outside"))
cap_gain %<>% mutate(ordinary = str_detect(text, "ordinary|regular"))
cap_gain %<>% mutate(however = str_detect(text, "However|however|How- ever|How­ ever"))

ordinary <- cap_gain %>% filter(ordinary == TRUE & however == FALSE)
cap_gains_tax_rates <- read_csv(here("data-created/cap_gains_rates.csv"))

cap_gain %<>% left_join(cap_gains_tax_rates[c("iso3c", "year", "appl_rate")], by = c("iso3c", "year"))
cap_gain %<>% rename("rate" = "appl_rate")

cap_gain %<>% mutate(note = case_when((not_taxed == TRUE & 
                                             however == FALSE & 
                                             nonresident == FALSE &
                                             no_sent < 4) |
                                        rate == 0 ~ "exempt",
                                      ordinary == TRUE & 
                                             however == FALSE & 
                                             nonresident == FALSE &
                                             no_sent < 4 ~ "ordinary"))


cap_gain %<>% mutate(land_rich = NA, 
                     shares = NA,
                     land_rich_indirect = NA,
                     shares_indirect = NA)


```

I assume that when there is just a reference that capital gains are taxed as ordinary business profits, then this excludes gains that non-residents without a permanent establishment in the country derive from selling a local company or a foreign company.

Brazil levies a higher rate when capital gains are derived by non-residents in low-tax jurisdictions (25% instead of 15%). However, the lower rate is coded here, since it is more likely to be relevant for the treaty shopping scenario, where the ultimate residents are located in capital exporting jurisdictions.
Italy only levies tax on sales by non-residents if located in a tax haven (27% in 2004), may prevent indirect transfers

Still to check: France

Some indirect transfer rules that are known to exist are not included here: China, Colombia, Senegal, United States

Costa Rica, gains other than from trading are maybe exempt before 2019. Check that

Czech Republic, from 2009 on gains on shares are exempt if seller is located in EU (so a bilateral adjustment may be necessary). In Spain, there are special rules for EU shareholders as well.


```{r capital gains functions}



amend_cols <- function(cap_gain, iso3c, years, columns = "all", value){
  
if ("all" %in% columns) {
  columns <- which(colnames(cap_gain) %in% c("land_rich", "shares"))

} else {
    columns <- which(colnames(cap_gain) %in% columns)
}

  rows <- which(cap_gain$iso3c == iso3c & cap_gain$year %in% years)

cap_gain[rows, columns] <- value
return(cap_gain)
}


add_note <- function(cap_gain, iso3c, years, note){
  rows <- which(cap_gain$iso3c %in% iso3c & cap_gain$year %in% years)
  cap_gain$note[rows] <- note
  return(cap_gain)
}

change_rate <- function(cap_gain, iso3c, years, value = NA, percentage_adjustment = NA){
  rows <- which(cap_gain$iso3c == iso3c & cap_gain$year %in% years)
  if (is.numeric(value)) {
  cap_gain$rate[rows] <- value
  }
  
  if (!is.na(percentage_adjustment)) {
     cap_gain$rate[rows] <- cap_gain$rate[rows] * percentage_adjustment
  }
  
  return(cap_gain)
}

```


```{r capital gain handcoded}


# Aruba
cap_gain %<>% add_note("ABW", c(2006:2021), "ordinary")

# Afghanistan
cap_gain %<>% add_note("AFG", c(2011:2019), "ordinary")

# Angola
cap_gain %<>% add_note("AGO", c(2004:2011), "exempt") # only sale of fixed assets are mentioned

cap_gain %<>% change_rate("AGO", c(2012:2021), 10) 
cap_gain %<>% add_note("AGO", c(2012:2021), "ordinary") 

#Albania
cap_gain %<>% add_note("ALB", c(2010:2014), "included") # according to administrative guidance
cap_gain %<>% add_note("ALB", c(2015:2018), "exempt") # only included in case of PE or domestic buyer
cap_gain %<>% add_note("ALB", c(2019:2021), "land-rich_direct_indirect") 

# Netherlands Antilles
cap_gain %<>% add_note("ANT", c(2004:2010), "exempt") # exemption for offshore companies mentioned


# Argentina
cap_gain %<>% add_note("ARG", c(2004:2010), "included") # specific rule for non-Argentine companies, seems not to include indirect transfers
cap_gain %<>% add_note("ARG", c(2011:2013), "exempt") 
cap_gain %<>% add_note("ARG", c(2014:2018), "included") 
cap_gain %<>% add_note("ARG", c(2019:2021), "included-indirect") 
cap_gain %<>% change_rate("ARG", c(2014:2021), 13.5) 

# Armenia
cap_gain %<>% add_note("ARM", c(2011:2021), "ordinary") 

#Australia
cap_gain %<>% add_note("AUS", c(2004:2007), "included") 
cap_gain %<>% add_note("AUS", c(2008:2021), "land-rich_direct_indirect") 

#Austria
cap_gain %<>% add_note("AUT", c(2004:2021), "ordinary") 


# Belgium
cap_gain %<>% add_note("BEL", c(2004:2021), "ordinary") 
cap_gain %<>% change_rate("BEL", c(2015:2018), value = 0.412) 
cap_gain %<>% change_rate("BEL", c(2019:2021), value = 15) 


# BES 
cap_gain %<>% add_note("BES", c(2011:2021), "exempt") # foreign companies subject to Netherlands tax regime (which exempts capital gains by non-residents)

# Bangladesh
cap_gain %<>% add_note("BGD", c(2004:2006), "ordinary") 
cap_gain %<>% change_rate("BGD", c(2005:2006), 10) 
cap_gain %<>% add_note("BGD", c(2019:2021), "included-indirect") 

# Bulgaria
 
cap_gain %<>% add_note("BGR", c(2004:2008), "included") 
cap_gain %<>% change_rate("BGR", c(2004), 15)
cap_gain %<>% add_note("BGR", c(2009:2021), "ordinary")

# Belarus
cap_gain %<>% add_note("BLR", c(2008:2021), "included") 
cap_gain %<>% change_rate("BLR", c(2010), 15)
cap_gain %<>% change_rate("BLR", c(2011:2012), 12)

# Bolivia
cap_gain %<>% add_note("BOL", c(2006:2021), "ordinary")

# Brazil
cap_gain %<>% add_note("BRA", c(2007:2021), "included") 
cap_gain %<>% change_rate("BRA", c(2016), 15)
cap_gain %<>% change_rate("BRA", c(2017:2021), 22.5)

# Brunei Darussalam

cap_gain %<>% add_note("BRN", c(2004:2021), "exempt") 

# Botswana
cap_gain %<>% change_rate("BWA", c(2004), 12.5)
cap_gain %<>% change_rate("BWA", c(2005:2011), 18.75)
cap_gain %<>% change_rate("BWA", c(2005:2011), 18.75)
cap_gain %<>% change_rate("BWA", c(2012:2014), 16.5)
cap_gain %<>% change_rate("BWA", c(2015:2021), 22.5)

cap_gain %<>% add_note("BWA", c(2004:2014), "ordinary") 
cap_gain %<>% add_note("BWA", c(2015:2021), "included") 

# Canada 

cap_gain %<>% add_note("CAN", c(2004:2010), "included-land-rich-indirect") 
cap_gain %<>% add_note("CAN", c(2011:2021), "land-rich_direct_indirect") # only included in case of PE or domestic buyer

# Switzerland

cap_gain %<>% add_note("CHE", c(2004:2021), "ordinary") 

# Chile
cap_gain %<>% add_note("CHL", c(2008:2010), "ordinary") 
cap_gain %<>% change_rate("CHL", c(2008:2010), 17)
cap_gain %<>% add_note("CHL", c(2011:2012), "included") 
cap_gain %<>% change_rate("CHL", c(2011:2014), 20)
cap_gain %<>% add_note("CHL", c(2013:2021), "included-indirect") 
cap_gain %<>% change_rate("CHL", c(2015:2016), 24)

# China
cap_gain %<>% add_note("CHN", c(2004:2021), "included") 


#Cote d'Ivoire
cap_gain %<>% add_note("CIV", c(2004:2021), "ordinary") 


# Cameroon
cap_gain %<>% add_note("CMR", c(2004:2013), "ordinary") 
cap_gain %<>% add_note("CMR", c(2014), "included") 
cap_gain %<>% add_note("CMR", c(2015:2021), "included-indirect") 
cap_gain %<>% change_rate("CMR", c(2015:2021), 16.5)

# DRC
cap_gain %<>% add_note("COD", c(2010:2021), "ordinary") 

# Congo Republic
cap_gain %<>% add_note("COG", c(2004:2013), "ordinary") 
cap_gain %<>% add_note("COG", c(2014:2021), "included") 
cap_gain %<>% change_rate("COG", c(2014:2021), 20)

# Colombia
cap_gain %<>% add_note("COL", c(2004:2021), "ordinary") 

# Cape Verde
cap_gain %<>% add_note("CPV", c(2010:2021), "included") 
cap_gain %<>% change_rate("CPV", c(2010:2021), 1)

# Costa Rica
cap_gain %<>% add_note("CRI", c(2004:2021), "ordinary") 
cap_gain %<>% change_rate("CRI", c(2019:2021), 15)

# Curacao
cap_gain %<>% add_note("CUW", c(2011:2021), "ordinary") 

# Cyprus
cap_gain %<>% add_note("CYP", c(2004:2016), "land-rich-direct") 
cap_gain %<>% add_note("CYP", c(2017:2021), "land-rich_direct_indirect") 

# Czech Republic
cap_gain %<>% add_note("CZE", c(2004:2008), "ordinary") 
cap_gain %<>% add_note("CZE", c(2009:2021), "included") 

# Germany
cap_gain %<>% add_note("DEU", c(2004:2021), "included") 
cap_gain %<>% change_rate("DEU", c(2004:2021), percentage_adjustment = 0.05)

# Denmark
cap_gain %<>% add_note("DNK", c(2004:2021), "exempt") 

# Dominican Republic
cap_gain %<>% add_note("DOM", c(2004:2006), "ordinary") 
cap_gain %<>% add_note("DOM", c(2007:2021), "included-indirect") 

# Algeria
cap_gain %<>% add_note("DZA", c(2012:2021), "included") 

# Ecuador
cap_gain %<>% add_note("ECU", c(2004:2015), "exempt") 
cap_gain %<>% add_note("ECU", c(2016:2021), "included-indirect") 

# Egypt
cap_gain %<>% add_note("EGY", c(2004:2014), "ordinary") 
cap_gain %<>% add_note("EGY", c(2015:2021), "included") 

# Spain
cap_gain %<>% add_note("ESP", c(2004:2021), "included") 
cap_gain %<>% change_rate("ESP", c(2007:2009), value = 18)
cap_gain %<>% change_rate("ESP", c(2010:2011), value = 19)
cap_gain %<>% change_rate("ESP", c(2012:2014), value = 21)
cap_gain %<>% change_rate("ESP", c(2015), value = 20)
cap_gain %<>% change_rate("ESP", c(2016:2021), value = 19)

# Estonia
cap_gain %<>% add_note("EST", c(2004:2021), "land-rich-direct") 

#Ethiopia
cap_gain %<>% add_note("ETH", c(2004:2017), "ordinary") 

# Finland
cap_gain %<>% add_note("FIN", c(2005:2021), "land-rich-direct") 

# Fiji
cap_gain %<>% add_note("FJI", c(2004:2010), "exempt") 
cap_gain %<>% add_note("FJI", c(2011:2021), "ordinary") 

# France


# Gabon
cap_gain %<>% add_note("GAB", c(2004:2021), "ordinary") 

# United Kingdom
cap_gain %<>% add_note("GBR", c(2004:2018), "exempt") 
cap_gain %<>% add_note("GBR", c(2019:2021), "land-rich_direct_indirect") 


# Georgia
cap_gain %<>% add_note("GEO", c(2004:2018), "ordinary") 
cap_gain %<>% add_note("GEO", c(2019:2021), "included") 

# Ghana
cap_gain %<>% add_note("GHA", c(2004:2021), "ordinary") 
cap_gain %<>% change_rate("GHA", c(2019:2021), value = 25)

# Guinea
cap_gain %<>% add_note("GIN", c(2004:2021), "ordinary") 
cap_gain %<>% change_rate("GIN", c(2012:2021), value = 10)

# Equatorial Guinea
cap_gain %<>% add_note("GNQ", c(2004:2021), "ordinary") 

# Greece
cap_gain %<>% add_note("GRC", c(2004:2013), "included") 
cap_gain %<>% add_note("GRC", c(2014:2020), "ordinary") 
cap_gain %<>% add_note("GRC", c(2021), "exempt") 

# Guatemala
cap_gain %<>% add_note("GTM", c(2004:2012), "ordinary") 
cap_gain %<>% add_note("GTM", c(2013:2021), "included-land-rich-indirect") 

# Guyana
cap_gain %<>% add_note("GUY", c(2004:2021), "ordinary") 

# Guam same as US, add Guam to the US entry

# Honduras
cap_gain %<>% add_note("HND", c(2004:2012), "ordinary") 
cap_gain %<>% add_note("HND", c(2013:2016), "exempt") 
cap_gain %<>% add_note("HND", c(2017:2021), "included") 

# Croatia
cap_gain %<>% add_note("HRV", c(2004:2021), "ordinary") 

# Hungary
cap_gain %<>% add_note("HUN", c(2004:2009), "exempt") 
cap_gain %<>% add_note("HUN", c(2010:2021), "land-rich-direct") 

# Indonesia
cap_gain %<>% add_note("IDN", c(2004:2021), "included") 
cap_gain %<>% change_rate("IDN", c(2004:2021), value = 20)

# India
cap_gain %<>% add_note("IND", c(2004:2012), "included")
cap_gain %<>% add_note("IND", c(2013:2021), "included-indirect")

# Ireland
cap_gain %<>% add_note("IRL", c(2004:2021), "land-rich_direct") #indirect is not specifically mentioned, although it could be interpreted as if falling under the definition ("shares deriving value from land")

# Iran
cap_gain %<>% add_note("IRN", c(2004:2006), "exempt")

# Iraq
cap_gain %<>% add_note("IRQ", c(2004:2021), "exempt")

# Iceland
cap_gain %<>% add_note("ISL", c(2004:2021), "ordinary")

# Isreal
cap_gain %<>% add_note("ISR", c(2004:2021), "included-indirect")

# Italy
cap_gain %<>% add_note("ITA", c(2004:2021), "exempt")
cap_gain %<>% add_note("ITA", c(2005:2021), "included")
cap_gain %<>% change_rate("ITA", c(2005:2007), value = 13.2) # 33% on 40% of the gain
cap_gain %<>% change_rate("ITA", c(2008:2016), value = 13.67)
cap_gain %<>% change_rate("ITA", c(2017:2017), value = 11.9)
cap_gain %<>% change_rate("ITA", c(2018), value = 13.95)
cap_gain %<>% change_rate("ITA", c(2019:2021), value = 26)

# Jamaica
cap_gain %<>% add_note("JAM", c(2004:2021), "ordinary")
cap_gain %<>% change_rate("JAM", c(2004:2009), value = 7.5) # no capital gains tax but a transfer tax on land and securities
cap_gain %<>% change_rate("JAM", c(2010:2014), value = 4)
cap_gain %<>% change_rate("JAM", c(2015:2018), value = 5)
cap_gain %<>% change_rate("JAM", c(2019:2021), value = 2)

# Jordan
cap_gain %<>% add_note("JOR", c(2004), "included")
cap_gain %<>% change_rate("JOR", c(2004), percentage_adjustment = 0.25)
cap_gain %<>% add_note("JOR", c(2005:2021), "exempt") # certain types of companies are not exempt (mainly banking sector)

# Japan
cap_gain %<>% add_note("JPN", c(2004:2021), "ordinary")

#Kazakhstan
cap_gain %<>% add_note("KAZ", c(2004:2011), "ordinary")
cap_gain %<>% add_note("KAZ", c(2012:2021), "included")

# Kenya
cap_gain %<>% add_note("KEN", c(2007, 2015:2021), "ordinary")
cap_gain %<>% add_note("KEN", c(2008:2014), "exempt")

# Cambodia
cap_gain %<>% add_note("KHM", c(2004:2021), "ordinary")

# Kosovo
cap_gain %<>% add_note("KSV", c(2014:2021), "exempt")

# Kuwait
cap_gain %<>% add_note("KWT", c(2004:2021), "included")

#Laos
cap_gain %<>% add_note("LAO", c(2004:2021), "included")
cap_gain %<>% change_rate("LAO", c(2004:2019), value = 10)
cap_gain %<>% change_rate("LAO", c(2020:2021), value = 2)

#Lebanon
cap_gain %<>% add_note("LBN", c(2004:2021), "exempt") #only fixed assets are taxed

# St. Lucia
cap_gain %<>% add_note("LCA", c(2014:2021), "exempt")

# Liechtenstein
cap_gain %<>% add_note("LIE", c(2004:2010), "ordinary")
cap_gain %<>% add_note("LIE", c(2011:2021), "exempt")

# Sri Lanka
cap_gain %<>% add_note("LKA", c(2004:2017), "exempt")
cap_gain %<>% add_note("LKA", c(2018:2021), "ordinary")

# Lithuania
cap_gain %<>% add_note("LTU", c(2004:2021), "ordinary")

#Luxembourg
cap_gain %<>% add_note("LUX", c(2004:2021), "exempt") # according to IBFD, assumed to have been like this always. Corporate tax guide only talks about regime for resident companies

#Latvia

cap_gain %<>% add_note("LVA", c(2004:2007), "exempt")
cap_gain %<>% add_note("LVA", c(2008:2021), "land-rich_direct_indirect")
cap_gain %<>% change_rate("LVA", c(2004:2017), value = 2)
cap_gain %<>% change_rate("LVA", c(2018:2021), value = 3)

# Macau
cap_gain %<>% add_note("MAC", c(2004:2021), "exempt")

#Saint-Martin
cap_gain %<>% add_note("MAF", c(2017:2021), "ordinary")

#Morocco
cap_gain %<>% add_note("MAR", c(2004:2006), "ordinary")
cap_gain %<>% add_note("MAR", c(2007:2021), "included")

#Monaco
cap_gain %<>% add_note("MCO", c(2004:2021), "ordinary")

#Moldova
cap_gain %<>% add_note("MDA", c(2004:2021), "ordinary")

#Madagascar
cap_gain %<>% add_note("MDG", c(2004:2019), "ordinary")
cap_gain %<>% add_note("MDG", c(2020:2021), "land-rich_direct_indirect")

#Maldives
cap_gain %<>% add_note("MDV", c(2004:2020), "exempt")
cap_gain %<>% add_note("MDV", c(2021), "ordinary")
cap_gain %<>% change_rate("MDV", c(2021), value = 15)

# Mexico
cap_gain %<>% add_note("MEX", c(2004:2015), "ordinary")
cap_gain %<>% add_note("MEX", c(2016:2021), "included")
cap_gain %<>% change_rate("MEX", c(2016:2021), value = 35)

#Macedonia
cap_gain %<>% add_note("MKD", c(2004:2009), "ordinary")
cap_gain %<>% add_note("MKD", c(2010:2014), "exempt")
cap_gain %<>% change_rate("MKD", c(2008:2009), percentage_adjustment = 0.7)

#Malta
cap_gain %<>% add_note("MLT", c(2004:2021), "land-rich-direct")

#Myanmar
cap_gain %<>% add_note("MMR", c(2004:2021), "included")

#Montenegro
cap_gain %<>% add_note("MNE", c(2004:2006), "included")
cap_gain %<>% add_note("MNE", c(2017:2021), "included")

#Mongolia
cap_gain %<>% add_note("MNG", c(2012:2021), "included")

#Northern Mariana (refer to US)

#Mozambique
# no specific mentioning of capital gains tax rate until 2013, therefore assumed to be ordinary (since a rate is specified in the at a glance table)

cap_gain %<>% add_note("MOZ", c(2004:2013), "ordinary")
cap_gain %<>% add_note("MOZ", c(2014:2021), "included-indirect")

#Mauritania
cap_gain %<>% add_note("MRT", c(2004:2021), "ordinary")

#Mauritius
cap_gain %<>% add_note("MUS", c(2004:2021), "exempt")

#Malawi
cap_gain %<>% add_note("MWI", c(2004:2021), "ordinary")

#Malaysia
# only mentioninig of real property gains tax, which would also apply to non-companies that hold real estate. 

cap_gain %<>% add_note("MYS", c(2004:2019), "land-rich-direct")
cap_gain %<>% add_note("MYS", c(2020:2021), "land-rich_direct_indirect")
cap_gain %<>% change_rate("MYS", c(2004:2010), value = 5)
cap_gain %<>% change_rate("MYS", c(2020:2021), value = 30)

# Namibia
cap_gain %<>% add_note("NAM", c(2004:2011), "exempt")
cap_gain %<>% add_note("NAM", c(2012:2015), "land-rich-direct") # only mineral companies though
cap_gain %<>% add_note("NAM", c(2016:2021), "land-rich_direct_indirect") # only mineral companies though


cap_gain %<>% change_rate("NAM", c(2012:2021), value = stat_rates$standard_rate[which(stat_rates$iso3c == "NAM" & stat_rates$year %in% (2012:2012))])

#New Caledonia
cap_gain %<>% add_note("NCL", c(2018:2021), "land-rich-direct")

#Nigeria
cap_gain %<>% add_note("NGA", c(2004:2021), "exempt")

#Nicaragua
cap_gain %<>% add_note("NIC", c(2013:2021), "included")
cap_gain %<>% change_rate("NIC", c(2013:2016), value = 10)

#Netherlands
cap_gain %<>% add_note("NLD", c(2004:2021), "ordinary")

#Norway
cap_gain %<>% add_note("NOR", c(2004:2008, 2012:2021), "exempt")
cap_gain %<>% add_note("NOR", c(2009:2011), "ordinary")
cap_gain %<>% change_rate("NOR", c(2009:2011), percentage_adjustment = 0.03)

#Nepal
cap_gain %<>% add_note("NPL", c(2006), "exempt")

#New Zealand
cap_gain %<>% add_note("NZL", c(2004:2021), "exempt")

#Oman
cap_gain %<>% add_note("OMN", c(2004:2021), "ordinary")

#Pakistan
cap_gain %<>% add_note("PAK", c(2004:2021), "ordinary")
cap_gain %<>% change_rate("PAK", c(2004:2010), percentage_adjustment = 0.75)
cap_gain %<>% change_rate("PAK", c(2011:2021), value = stat_rates$rate[which(stat_rates$iso3c == "PAK" & stat_rates$year %in% (2011:2021))] * 0.75)

#Panama
cap_gain %<>% add_note("PAN", c(2004:2006), "exempt")
cap_gain %<>% add_note("PAN", c(2006:2013), "included")
cap_gain %<>% add_note("PAN", c(2014:2021), "included-indirect")
cap_gain %<>% change_rate("PAN", c(2006:2021), value = 10)

#Peru
cap_gain %<>% add_note("PER", c(2009:2010), "included")
cap_gain %<>% add_note("PER", c(2011:2021), "included-indirect")
cap_gain %<>% change_rate("PER", c(2010:2021), value = 30)

#Philippines
cap_gain %<>% add_note("PHL", c(2004:2021), "ordinary")
cap_gain %<>% change_rate("PHL", c(2004:2021), value = 10)

#Poland
cap_gain %<>% add_note("POL", c(2004:2006), "ordinary")
cap_gain %<>% add_note("POL", c(2007:2021), "included")

#Puerto Rico
cap_gain %<>% add_note("PRI", c(2004:2005), "included-indirect")
cap_gain %<>% add_note("PRI", c(2006:2021), "ordinary")
cap_gain %<>% change_rate("PRI", c(2004:2005), value = 12.5)

#Portugal
cap_gain %<>% add_note("PRT", c(2004:2021), "land-rich_direct_indirect") # For companies situated in blacklisted territories, transfers of other shares are taxed as well
cap_gain %<>% change_rate("PRT", c(2014:2021), value = 25)

#Paraguay
cap_gain %<>% add_note("PRY", c(2004:2021), "ordinary")
cap_gain %<>% change_rate("PRY", c(2004:2021), value = stat_rates$rate[which(stat_rates$iso3c == "PRY" & stat_rates$year %in% (2004:2021))])

#Palestinian Territories
cap_gain %<>% add_note("PSE", c(2013:2014), "ordinary")
cap_gain %<>% change_rate("PSE", c(2013:2014), percentage_adjustment = 0.25)
cap_gain %<>% add_note("PSE", c(2015:2021), "exempt")

#Qatar
cap_gain %<>% add_note("QAT", c(2013:2021), "included")

#Romania
cap_gain %<>% add_note("ROU", c(2004:2004), "included-land-rich-indirect")
cap_gain %<>% add_note("ROU", c(2005:2007), "ordinary")
cap_gain %<>% add_note("ROU", c(2008:2013), "included-land-rich-indirect")
cap_gain %<>% add_note("ROU", c(2014:2021), "exempt")

#Russia
cap_gain %<>% add_note("RUS", c(2004:2015), "ordinary")
cap_gain %<>% add_note("RUS", c(2016:2021), "land-rich_direct_indirect")

#Rwanda
cap_gain %<>% add_note("RWA", c(2004:2021), "ordinary")

#Saudi Arabia
cap_gain %<>% add_note("SAU", c(2005:2020), "included")
cap_gain %<>% add_note("SAU", c(2021), "ordinary")

#Sudan
cap_gain %<>% add_note("SDN", c(2004:2006), "exempt")

#Singapore
cap_gain %<>% add_note("SGP", c(2018:2021), "exempt")


#Senegal
cap_gain %<>% add_note("SEN", c(2004:2021), "ordinary")
#but in 2019 indirect transfer rule was introduced

#El Salvador
cap_gain %<>% add_note("SLV", c(2004:2021), "ordinary")
cap_gain %<>% change_rate("SLV", c(2008:2021), value = 10)

#Serbia
cap_gain %<>% add_note("SRB", c(2011:2021), "included")
cap_gain %<>% change_rate("SRB", c(2011:2013), value = 20)

#South Sudan
cap_gain %<>% add_note("SSD", c(2014:2021), "ordinary")

#Sao Tome
cap_gain %<>% add_note("STP", c(2017:2021), "ordinary")

#Suriname
cap_gain %<>% add_note("SUR", c(2004:2021), "ordinary")

#Slovak Republic
cap_gain %<>% add_note("SVK", c(2004:2017), "ordinary")
cap_gain %<>% add_note("SVK", c(2018:2021), "included")

#Slovenia
cap_gain %<>% add_note("SVN", c(2004:2021), "ordinary")

#Sweden
cap_gain %<>% add_note("SWE", c(2004:2021), "exempt")

#Sint Maarten
cap_gain %<>% add_note("SXM", c(2011:2021), "ordinary")

#Syria
cap_gain %<>% add_note("SYR", c(2005:2011), "exempt")

#Chad
cap_gain %<>% add_note("TCD", c(2013:2021), "ordinary")

#Trinidad and Tobago
cap_gain %<>% add_note("TTO", c(2004:2021), "exempt")

#Tunisia
cap_gain %<>% add_note("TUN", c(2012:2021), "included")

#Turkey
cap_gain %<>% add_note("TUR", c(2004:2021), "included")
cap_gain %<>% change_rate("TUR", c(2007:2010), value = stat_rates$rate[which(stat_rates$iso3c == "TUR" & stat_rates$year %in% (2007:2010))])

#Taiwan
cap_gain %<>% add_note("TWN", c(2004:2021), "exempt")

#Tanzania
cap_gain %<>% add_note("TZA", c(2004:2014), "ordinary")
cap_gain %<>% add_note("TZA", c(2015:2021), "included-indirect")

#Uganda
cap_gain %<>% add_note("UGA", c(2004:2018), "ordinary") # according to EY shares are only included since 2017, but according other guide, the notion of business assets applied to shares before. Zain case also shows that tax authority was seeking to tax this
cap_gain %<>% add_note("UGA", c(2019:2021), "included-indirect") #https://www.bdo.global/en-gb/microsites/tax-newsletters/corporate-tax-news/issue-50-february-2019/uganda-taxation-of-indirect-transfers-in-uganda

#Ukraine
cap_gain %<>% add_note("UKR", c(2014:2020), "ordinary") 
cap_gain %<>% add_note("UKR", c(2021), "included-land-rich-indirect")

#United States, Guam, Mariana Islands and US Virgin Islands
cap_gain %<>% add_note(c("USA", "GUM", "MNP", "VIR"), c(2004:2021), "ordinary")

#Uzbekistan
cap_gain %<>% add_note("UZB", c(2013:2021), "included")
cap_gain %<>% change_rate("UZB", c(2013:2021), value = 20)

#Venezuela
cap_gain %<>% add_note("VEN", c(2004:2021), "ordinary")

#Vietnam
cap_gain %<>% add_note("VNM", c(2004:2008), "included")
cap_gain %<>% add_note("VNM", c(2009:2011), "ordinary")
cap_gain %<>% add_note("VNM", c(2012:2021), "included")
# one could argue that they are since 2012 de facto exempt, since only a gross rate of 0.1% on the share price is levied

#South Africa
cap_gain %<>% add_note("ZAF", c(2004:2021), "land-rich_direct_indirect")

#Zimbabwe
cap_gain %<>% add_note("ZWE", c(2004:2021), "ordinary")


```


```{r manual changes based on other literature}


# China
cap_gain %<>% add_note("CHN", c(2010:2021), "included-indirect") 

#Colombia
cap_gain %<>% add_note("COL", c(2019:2021), "included-indirect") 

#Japan

#Tanzania

#Senegal
cap_gain %<>% add_note("SEN", c(2019:2021), "land-rich_direct_indirect") 

#United States
cap_gain %<>% add_note(c("USA", "GUM", "MNP", "VIR"), c(2004:2021), "land-rich-direct")


```



```{r finalize capital gains table}


# Assume that non-residents are taxed under the rules applying to all taxpayers, use coalesce

cap_gain %<>% mutate(land_rich = ifelse(note == "exempt", 0, rate))

cap_gain %<>% mutate(shares = ifelse(note %in% c("exempt", "land-rich-direct"), 0, rate))

cap_gain %<>% mutate(land_rich_indirect = ifelse(note %in% c("land-rich_direct_indirect", "included-land-rich-indirect", "included-indirect"), rate, 0))

cap_gain %<>% mutate(shares_indirect = ifelse(note == "included-indirect", rate, 0))

# Chile different values for different types of capital gains
cap_gain %<>% amend_cols("CHL", c(2013:2021), columns = c("land_rich_indirect", "shares_indirect"), value = 35)

# standardize table format

cap_gain %<>% rename(explanation = text)

cap_gain %<>% select(iso3c, year, explanation, note, land_rich, land_rich_indirect, shares, shares_indirect)

cap_gain %<>% pivot_longer(cols = c("land_rich", "land_rich_indirect", "shares", "shares_indirect"), names_to = "category", values_to = "rate")

write_csv(cap_gain, here("data-created/cap_gains_non_residents.csv"))

```



