---
title: "Special regimes conduits"
author: "Frederik Heitmüller"
date: "2022-10-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require('here')) install.packages('here'); library('here') 
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse') 
if (!require('magrittr')) install.packages('magrittr'); library('magrittr') 
if (!require('countrycode')) install.packages('countrycode'); library('countrycode') 
if (!require('purrr')) install.packages('purrr'); library('purrr') 
if (!require('stringr')) install.packages('stringr'); library('stringr') 
devtools::load_all()

# defining for which data years the script should run
years <- c(2004:2021)
```


Special regimes that provide for wth exemptions, such as headquarter regime in South Africa. 

Still to check: Honduras
```{r special regimes}
all_paras <- read_csv(here("data-created/all_paras_ey.csv"))
all_paras %<>% mutate(heading = tolower(heading))
all_paras %<>% filter(!str_detect(heading, "%"))
all_paras$heading %<>% str_replace("\\.", "") 
all_paras$heading %<>% trimws()
 #maybe eliminate characters of "- " preceded by a letter
all_paras$text %<>% str_replace_all("(?<=[:alpha:])- ", "")


para_special_regimes <- c("foreign-source interest income exclusion", "foreign derived intangible income and global intangible low-taxed income deduction", "incentives for hub services", "incentives",  "intellectual property", "knowledge development box",  "non-domicile rule", "other tax benefits", "tax incentives")

special <- all_paras %>% filter(heading %in% para_special_regimes | 
                        str_detect(heading, "exempt|holding|headquarter|international|regime|box|conduit|intermediate|vehicle|offshore|zone|innovation") |
                          str_detect(text, "international business|International Business"))


special %<>% filter(!str_detect(heading, "withholding|avoidance|compliance assurance|financial reporting|tax haven|depreciation|currenc|limitation|group|restriction|foreign-exchange|types of companies|nature of tax|deductibility|capital gains|debt-to-equity|transfer pricing|expense|simplified|mandatory disclosure|payments|merger|business combinations|closely held companies|law 89/1967|employee|individual|participation exemption"))
special %<>% filter(!heading %in% c("dividends", "dividends and interest", "rates", "rate", "rates of tax"))


stat_rates <- read_csv(here("data-created/ey_stat_rates.csv"))
special %<>% left_join(stat_rates[c("iso3c", "year", "rate")])

all_tocs <- readRDS(here("data-created/tocs.rds"))
special <- left_join(all_tocs, special, by = c("iso3c", "year"))
special %<>% group_by(iso3c, heading) %>% arrange(year, .by_group = TRUE)

special$text %<>% trimws()
special$text %<>% replace_na("blank")
special %<>% mutate(same_t = NA)
for (i in 2:nrow(special)) {
  if (special$text[i] == special$text[i - 1]) {
    special$same_t[i] <- "same" 
  } else {
    special$same_t[i] <- "change" 
  }
}

```

What to do with IP boxes with nexus requirements. If grandfathering of old regime, then code up to that date. If nexus requirement add it to the code.
Make special analysis of Australian dividend regime, where conduit dividend income maybe exempt from taxes on receipt and withholding

Lebanon special offshore holding regime
Monaco foreign source income (except royalties) exemption regime

```{r special regimes handcoded}

all_tocs <- readRDS(here("data-created/tocs.rds"))
special <- all_tocs
stat_rates <- read_csv(here("data-created/statutory_rates.csv"))
cap_gains_rates <- read_csv(here("data-created/cap_gains_rates.csv"))
special %<>% left_join(stat_rates[c("iso3c", "year", "comb_rate")])
special %<>% left_join(cap_gains_rates[c("iso3c", "year", "appl_rate")])
special %<>% mutate(appl_rate = coalesce(appl_rate, comb_rate))


instructions <- list(
list("ABW", c(2011:2021), "special tax regimes for certain companies", c("all_rec", "div_wth"), value = 0, "rate", NA),
list("ALB", c(2018:2021), "tax incentives", c("roy_rec"), 5, "rate", NA), # software companies
list("ANT", c(2004:2010), "tax incentives", c("all_rec"), 2, "rate", NA), # e-zone
list("AUS", c(2006:2021), "foreign conduit income", c("div_wth"), 0, "rate", NA), # foreign conduit income
list("BEL", c(2008:2021), "patent box", c("roy_rec"), 80, "percentage", NA), # grandfathered until 2021
list("BEL", c(2016:2021), "innovation deduction", c("roy_rec"), 85, "percentage", "nexus"),
list("BGD", c(2019:2021), "tax incentives", c("roy_rec", "ser_rec"), 0, "rate", NA), # software development and computer services exemption
list("BLR", c(2009:2021), "special tax regimes", c("roy_rec"), 0, "rate", NA), # high technology park
list("BRB", c(2004:2021), "international business", c("all_rec"), 1, "rate", NA), # international business companies, grandfathered until June 2021
list("BRB", c(2004:2021), "international business", c("all_wth"), 0, "rate", NA), # international business companies, grandfathered until June 2021
list("CHE", c(2004:2019), "holding companies", c("div_rec", "cap_rec"), 0, "rate", NA),
list("CHE", c(2004:2019), "holding companies", c("int_rec", "roy_rec"), 7.8, "rate", NA),
list("CHL", c(2004:2021), "chilean holding company regime", c("all_rec", "div_wth", "cap_wth"), 0, "rate", NA), # grandfathered for the years 2018:2021, apparently could not be used for treaty shopping since holding were not considered Chilean residents https://www.derechotributario.cl/2006/11/sociedad-plataforma-una-idea-frustrada/
list("CHN", c(2010:2021), "tax incentives", c("roy_rec"), 0, nexus = "nexus", "rate", NA),
list("COL", c(2019:2021), "colombian holding company regime", c("div_rec", "cap_rec", "div_wth", "cap_wth"), 0, "rate", NA),
list("CPV", c(2016:2021), "international business center", c("ser_rec"), 2.5, "rate", NA),
list("CPV", c(2016:2021), "international business center", c("div_wth", "cap_wth"), 0, "rate", NA),
list("CRI", c(2004:2019), "free trade zone regime", c("all_rec"), 0, "rate", NA),
list("CRI", c(2020:2021), "free trade zone regime", c("all_rec"), 0, "rate", nexus = "nexus"),
list("CUW", c(2011:2021), "tax incentives", c("all_rec"), 2, "rate", NA), # grandfathered until 2022
list("ESP", c(2004:2021), "foreign portfolio holding company regime", c("div_wth", "cap_wth"), 0, "rate", NA),
list("ESP", c(2016:2021), "patent box regime", c("roy_rec"), 60, "percentage", "nexus"),
list("GBR", c(2013:2015), "patent box", c("roy_rec"), 10, "rate", NA),
list("GBR", c(2016:2021), "patent box", c("roy_rec"), 10, "rate", nexus = "nexus"),
list("GGY", c(2004:2007), "exempt companies", c("all_rec"), 0, "rate", NA),
list("GIB", c(2004:2006), "exempt companies", c("all_rec", "div_wth", "int_wth"), 0, "rate", NA),
list("HKG", c(2004:2021), "territorial regime", c("all_rec"), 0, "rate", NA),
list("HUN", c(2004:2005), "tax incentives", c("all_rec"), 3, "rate", NA),
list("HUN", c(2004:2009), "tax incentives", c("int_rec", "roy_rec"), 50, "percentage", NA),
list("HUN", c(2010:2015), "tax incentives", c("roy_rec"), 50, "percentage", NA),
list("HUN", c(2010), "foreign-source interest income exclusion", c("int_rec"), 75, "percentage", NA),
list("HUN", c(2016:2021), "tax incentives", c("int_rec", "roy_rec"), 50, "percentage", "nexus"),
list("HUN", c(2004:2006), "exempt companies", c("all_rec"), 0, "rate", NA),
list("IMN", c(2004:2006), "exempt companies", c("all_rec", "all_wth"), 0, "rate", NA),
list("IND", c(2017:2021), "patent box regime", c("roy_rec"), 10, "rate", nexus = "nexus"),
list("IRL", c(2016:2021), "knowledge development box", c("roy_rec"), 6.25, "rate", nexus = "nexus"),
list("ISL", c(2004:2007), "international trading companies", c("all_rec"), 5, "rate", NA),
list("ITA", c(2015:2021), "patent box regime", c("roy_rec"), 50, "percentage", "nexus"),
list("JEY", c(2004:2008), "exempt companies", c("all_rec"), 0, "rate", NA),
list("JEY", c(2004:2011), "international business companies", c("all_rec"), 2, "rate", NA),
list("LBN", c(2004:2021), "offshore companies", c("all_rec", "div_wth"), 0, "rate", NA),
list("LCA", c(2014:2021), "international business companies", c("all_rec", "all_wth"), 0, "rate", NA),
list("LIE", c(2011:2020), "patent box regime for intellectual property companies", c("roy_rec"), 2.5, "rate", NA), #grandfathered since 2017
list("LKA", c(2008:2017), "tax incentives", c("all_rec"), 0, "rate", NA), # exemptions for income received from abroad
list("LKA", c(2018:2021), "tax incentives", c("all_rec"), 0, "rate", NA), # regional headquarter
list("LUX", c(2011:2021), "intellectual property", c("roy_rec", "cap_rec"), 80, "percentage", NA), #from 2016 grandafthered until 2021
list("LUX", c(2004:2010), "holding company", c("all_rec"), 0, "rate", NA), # grandfathered from 2006 onwards
list("LUX", c(2004:2021), "dividend distribution", c("div_wth"), 0, "rate", NA),# to qualifying participations 
list("MAC", c(2004:2020), "offshore companies", c("all_rec"), 0, "rate", NA), # repealed as of 2021
list("MAR", c(2004:2018), "tax incentives", c("all_rec"), 0, "rate", NA), # offshore companies, only nominal rate
list("MLT", c(2019:2021), "tax incentives", c("roy_rec"), 95, "percentage", "nexus"),
list("MUS", c(2019:2021), "partial exemption", c("div_rec","int_rec"), 80, "percentage", NA),
list("MUS", c(2004:2021), "Global Business Licence 1", c("all_rec"), 80, "percentage", NA), # grandfathered until 2021
list("MUS", c(2004:2021), "Global Business Licence 1", c("all_wth"), 0, "rate", NA), # grandfathered until 2021
list("MYS", c(2004:2010), "offshore financial center", c("all_rec","all_wth"), 0, "rate", NA),
list("MYS", c(2011:2019), "labuan international business and financial center", c("all_rec","all_wth"), 0, "rate", NA),
list("MYS", c(2019:2021), "labuan international business and financial center", c("int_rec", "div_rec", "cap_rec", "all_wth"), 0, "rate", NA),
list("MYS", c(2019:2021), "labuan international business and financial center", c("roy_rec", "ser_rec"), 3, "rate", NA),
list("NLD", c(2007:2010), "patent box", c("roy_rec"), 10, "rate", NA),
list("NLD", c(2010:2017), "innovation box", c("roy_rec"), 5, "rate", NA),
list("NLD", c(2018:2020), "innovation box", c("roy_rec"), 7, "rate", nexus = "nexus"),
list("NLD", c(2021), "innovation box", c("roy_rec"), 9, "rate", nexus = "nexus"),
list("PAN", c(2008:2018), "headquarters law", c("ser_rec"), 0, "rate", NA),
list("PAN", c(2019:2021), "headquarters law", c("ser_rec"), 5, "rate", NA),
list("QAT", c(2008:2021), "tax incentives", c("ser_rec"), 0, "rate", NA), # Qatar Science and Technology Park
list("SGP", c(2004:2021), "tax incentives", c("all_rec", "roy_wth", "ser_wth"), 0, "rate", NA), # headquarter program, remittance basis for taxation, approved royalties and technical services
list("SVK", c(2018:2021), "patent box", c("roy_rec"), 50, "percentage", nexus = "nexus"),
list("SXM", c(2011:2019), "offshore companies", c("all_rec"), 3, "rate", NA), # tax exempt companiesalso exist, but are not eligible for treaty benefits
list("THA", c(2016:2018), "tax incentives", c("roy_rec", "int_rec", "ser_rec"), 0, "rate", NA),
list("THA", c(2019:2021), "tax incentives", c("div_wth", "int_wth", "div_rec"), 0, "rate", NA),
list("THA", c(2019:2021), "tax incentives", c("roy_rec", "int_rec", "ser_rec"), 3, "rate", NA),
list("TUR", c(2005:2021), "international holding companies", c("cap_rec"), 0, "rate", NA),
list("VGB", c(2004:2005), "international business companies", c("all_rec"), 0, "rate", NA),
list("ZAF", c(2011:2021), "headquarter companies", c("div_wth"), 0, "rate", NA)
)
```

jersey general rate of 0 percent might not be adequately coded in statutory rates. Amend procedure to develop statutory rates table.


```{r test}


add_man <- function(instructions, special){
  iso3c <- instructions[[1]] 
  years <- instructions[[2]] 
  regime <- instructions[[3]] 
  payments <- instructions[[4]] 
  value <- instructions[[5]] 
  expressed_in <- instructions[[6]]
  nexus <- instructions[[7]]
  
  len <- length(years)
  
  if ("all_rec" %in% payments) {
    payments <- c(payments, "div_rec", "int_rec", "roy_rec", "ser_rec", "cap_rec")
    payments <- payments[-which(payments == "all_rec")]
  }

    if ("all_wth" %in% payments) {
    payments <- c(payments, "div_wth", "int_wth", "roy_wth", "ser_wth", "cap_wth")
    payments <- payments[-which(payments == "all_wth")]
  }
  
  addition <- data.frame(year = years)
  addition %<>% mutate(iso3c = iso3c, div_wth = NA, int_wth = NA, roy_wth = NA, ser_wth = NA, cap_wth = NA, div_rec = NA, int_rec = NA, roy_rec = NA, ser_rec = NA, cap_rec = NA, regime = regime, nexus = nexus)
  if (expressed_in == "rate") {
    addition %<>% mutate(across(all_of(payments), ~ value))
  }
  
    if (expressed_in == "percentage") {
    calc_values_cap <- special$appl_rate[which(special$iso3c == iso3c & special$year %in% years)] * ((100 - value)/100)
    calc_values_other <- special$comb_rate[which(special$iso3c == iso3c & special$year %in% years)] * ((100 - value)/100)
    
    if ("cap" %in% str_sub(payments, 1, 3)) {
      cap_payments <- payments[which(str_sub(payments, 1, 3) == "cap")]
      addition %<>% mutate(across(all_of(cap_payments), ~ calc_values_cap))
    }
    
     if (length(payments[which(str_sub(payments, 1, 3) != "cap")]) > 0) {
       other_payments <- payments[which(str_sub(payments, 1, 3) != "cap")]
       addition %<>% mutate(across(all_of(other_payments), ~ calc_values_other))
     }
  }
  
  return(addition)
}

special_regimes <- map(instructions, add_man, special)
special_regimes %<>% reduce(rbind)
write_csv(special_regimes, here("data-created/special_regimes.csv"))
```

