---
title: "Data Preparation SPE investments"
author: "Frederik Heitmüller"
date: "15 February 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(readxl)
library(magrittr)
library(countrycode)
library(ggpubr)
library(lubridate)
devtools::load_all()
```

Here a comprehensive dataset of outward SPE statistics from various jurisdictions is created. 

Data on Spanish FDI abroad separated by ETVE-status of companies was downloaded from the website of the [Spanish Ministry of Commerce](http://datainvex.comercio.es/) on 18 February 2022. Data was available up to for the period 2006 to 2019 on that date. 

The data by the Spanish Ministry of Commerce is expressed in Thousand Euros. Therefore, it is converted to Million USD using annual average exchange rate data from the OECD.

```{r Spanish data}


customcodes <- c("Antartida" = "ATA",
  "Antillas Neerlandesas" = "ANT",
  "Arabia Saudi" = "SAU",
  "Azerbaiyan" = "AZE",
  "Corea Del Norte" = "PRK",
  "Corea Del Sur" = "KOR",
  "Costa De Marfil" = "CIV",
  "Emiratos Arabes Unidos" = "ARE",
  "Fiyi" = "FJI",
  "Georgia Del Sur E Islas Sandwich Del Sur" = "SGS",
  "Guayana" = "GUY",
  "Isla De Man" = "IMN",
  "Isla Navidad" = "CXR",
  "Islas Caiman" = "CYM",
  "Islas Menores Alejadas De Ee.uu." = "UMI",
  "Islas Salomon" = "SLB",
  "Islas Turcas Y Caicos" = "TCA",
  "Islas Virgenes Britanicas" = "VGB",
  "Islas Virgenes De Los Estados Unidos" = "VIR",
  "Kazajstan" = "KAZ",
  "Kirguistan" = "KGZ",
  "Micronesia" = "FSM",
  "Paises Bajos" = "NLD",
   "Republica Centroafricana" = "CAF",
   "San Cristobal Y Nieves" = "KNA",
   "San Martin" = "MAF",
   "San Vicente Y Las Granadinas" = "VCT",
    "Santo Tome Y Principe" = "STP",
    "Tayikistan" = "TJK",
    "Territorio Britanico Del Oceano Indico" = "IOT",
    "Tunez" = "TUN"
)

exchangeratetable <- read_delim(here("data-raw/exchangerates.csv"), delim=",", col_names = TRUE)
exchangeratetable %<>% filter(LOCATION=="ESP")
exchangeratetable %<>% mutate_at(6, as.character)
exchangeratetable %<>% rename(exchangerate = Value)


span_stock <- read_excel(here("data-raw/fdi_data/consulta_datainvex.xls"), skip =1)

span_clean <- function(df, exchangeratetable, customcodes){
  df <- df[-1, -c(2, 3)]
  df %<>% pivot_longer(cols = c(2:ncol(df)), names_to = "year")
  df %<>% rename("country" = "Elemento")
  df$country = sapply(df$country, str_to_title)
  df %<>% mutate(iso3c = countrycode(coalesce(countryname(country), country), "country.name", "iso3c", custom_match = customcodes))
  df %<>% filter(year %in% c(2007:2019))
  #convert to USD

  df %<>% left_join(exchangeratetable[c("TIME", "exchangerate")], by=c("year"="TIME"))
  df %<>% mutate(value = as.numeric(value)/exchangerate) ##converting to US dollars
  df %<>% select(-exchangerate)

  #convert to million
  df %<>% mutate(value = value/1000)

  return(df)
}


span_stock <- span_clean(span_stock, exchangeratetable, customcodes)



span_spe <- span_stock %>% 
  filter(iso3c %in% host_country_data_available$iso3c) %>% 
  select(-country) %>% 
  rename("host" = "iso3c") %>% 
  add_column(type_fdi = "total", home = "ESP", indicator = "million_USD")

span_spe$year %<>% as.numeric
write_csv(span_spe, here("data-created/span_spe.csv"))


```

Data on the investments by Mauritian Global Business Companies 1 (GBC 1) was downloaded from the [Mauritius Financial Services Commission](https://www.fscmauritius.org/media/119927/value-of-investment-2012_2021i.xlsx) on 17 February 2022.I assume that all GBC 1 companies are special purpose entities.
Data still lists the Netherlands Antilles, which were separated into different entities in 2010. For the analysis, they are disregarded anyways since they .

```{r Mauritius data}

mauritius_spe <- read_excel(here("data-raw/fdi_data/value-of-investment-2012_2021i.xlsx"), sheet = 3, col_names = FALSE)
mauritius_spe[1, 1] <- "date"
mauritius_spe[1, which(is.na(mauritius_spe[1, ]))] <- mauritius_spe[1, which(is.na(mauritius_spe[1, ]))-1]
names(mauritius_spe)[4:ncol(mauritius_spe)] <- paste(mauritius_spe[2, 4:ncol(mauritius_spe)],
                                 mauritius_spe[1, 4:ncol(mauritius_spe)],
                                 sep = "_")
names(mauritius_spe)[1:3] <- mauritius_spe[2, 1:3]
mauritius_spe %<>% slice(-c(1:2))
mauritius_spe %<>% select(-1)
mauritius_spe %<>% filter(!is.na(Countries))
mauritius_spe %<>% pivot_longer(3:ncol(mauritius_spe))
mauritius_spe %<>% separate(name, into = c("indicator", "date"), sep = "_")
mauritius_spe %<>% mutate(year = year(as_date(as.numeric(date))),
                          month = month(as_date(as.numeric(date))))
mauritius_spe %<>% filter(month == 12)
mauritius_spe %<>% mutate(year = as.numeric(year)-70)
mauritius_spe %<>% mutate(host = countrycode(Code, "iso2c", "iso3c"))

mauritius_spe %<>% 
  select(indicator, value, year, host) %>%
  add_column(home = "MUS", type_fdi = "total")
mauritius_spe$value %<>% as.numeric
mauritius_spe$indicator %<>% recode("Direct Investment - Outward (USD Millions)" = "million_USD", "No. of GBC1s Involved" = "number_entities")
write_csv(mauritius_spe, here("data-created/mauritius_spe.csv"))


```


Eurostat data was downloaded from the table "bop_fdi6_pos". Data is in Million EUR, it therefore needs to be converted to USD dollar as well, in order to be compared and used together with data from other sources.

```{r eurostat and OECD data}

eurostat_spe_fdi <- read_csv(here("data-raw/fdi_data/eurostat_spe_fdi.csv"))
eurostat_spe_fdi$year %<>% as.numeric

eurostat_spe_fdi$type_fdi %<>% recode("DO__D__F" = "total") 

# eurostat needs to be converted to USD
exchangeratetable <- read_delim(here("data-raw/exchangerates.csv"), delim=",", col_names = TRUE)
exchangeratetable %<>% filter(LOCATION == "EA19")
eurostat_spe_fdi %<>% left_join(exchangeratetable[c("TIME", "Value")], by=c("year"="TIME"))
eurostat_spe_fdi %<>% mutate(value = value/Value) 
eurostat_spe_fdi %<>% select(-Value)
eurostat_spe_fdi$indicator %<>% recode("MIO_EUR" = "million_USD")

oecd_spe_fdi <- read_csv(here("data-raw/fdi_data/oecd_spe_fdi.csv"))
oecd_spe_fdi$type_fdi %<>% recode("LE_FA_F" = "total", "LE_FA_FL" = "debt", "LE_FA_F5" = "equity")

spe_fdi <- full_join(eurostat_spe_fdi, oecd_spe_fdi, by = c("home", "host", "type_fdi", "year", "indicator"))
spe_fdi %<>% rename("value_eurostat" = "value.x", "value_oecd" = "value.y")

# add Spanish data 
span_spe <- read_csv(here("data-created/span_spe.csv"))

spe_fdi %<>% full_join(span_spe, by = c("home", "host", "type_fdi", "year", "indicator"))
spe_fdi %<>% rename("value_spain" = "value")

#add Mauritius data
mauritius_spe <- read_csv(here("data-created/mauritius_spe.csv"))
spe_fdi %<>% full_join(mauritius_spe, by = c("home", "host", "type_fdi", "year", "indicator"))
spe_fdi %<>% rename("value_mauritius" = "value")

write_csv(spe_fdi, here("data-created/spe_fdi.csv"))
```

```{r make comparisons between different data values}

spe_fdi %<>% mutate(discrepancy = value_oecd/value_eurostat)


```

